### 2014-11-13 tex/intro.tex
Adjusted the contributions section to better highlight the strengths of our approach.

\item\textbf{-} A symbolic summary heap representing
sets of concrete heaps without overapproximation or restricting aliasing.
% supports aliasing, and and allows strong updates without auxiliary variables 
% or constraint rewriting.

% to handle alias and efficient updates of constraints.

\item\textbf{-} A algorithm to initialize, summarize, and
  update summary heaps during symbolic execution, without mutating 
  constraints or introducing auxiliary variables.

\item\textbf{-} A proof of the existence of a bisimulation relation to establish
  that the heap summary approach is sound and complete with respect to
  properties provable by GSE.

@@

>>>>

%\item\textbf{-} A summary heap that represents sets of concrete heaps
% without approximation or morphological restrictions.

\item\textbf{-} A non-approximate, morphologically arbitrary, and efficient 
summary heap representation.

\item\textbf{-} An algorithm to dynamically initialize, summarize, and
  update the summary heap during symbolic execution.

\item\textbf{-} A bisimulation proof establishing the soundness and 
completeness of the heap summary approach with respect to
properties provable by GSE.

@@

%\begin{compactdesc}
%
%\item\textbf{-} A summary heap as a bipartite graph that supports
%  aliasing and does not require rewriting of constraints.
%
%% to handle alias and efficient updates of constraints.
%
%\item\textbf{-} A summary heap algorithm to initialize, summarize, and
%  update the bipartiate graphs during symbolic execution.
%
%\item\textbf{-} A proof of the existence of a bisimulation relation to establish
%  that the heap summary approach is sound and complete with respect to
%  properties provable by GSE.
%
%\item\textbf{-} A proof of concept implementation and small empirical study to demonstrate the scability of the heap summary approach
%  compared to other GSE approaches.
%
%\end{compactdesc}
